### 2014-10-26 thesis/method/classification.tex
Added some section labels and updated some headings

\subsubsection{Ranked Distance}
\paragraph{Intuition}
As we mentioned earlier, all features are considered equally in a $k$-NN
classifier, which implies that all features are equally important in predicting
the class. In practice, however, this is not always the case: to predict the
LOS of a trauma patient, the severity of their injury should affect the final
LOS more than whether or not they can speak English (which could be just two
of many features that are recorded about a patient). Our contribution is thus
a modified distance function to take the relative importance of attributes into
account.

@@

\section{Conclusion}
In this chapter we have outlined all of the learning algorithms that we will
be evaluating with respect to our classification problem, from the simple
0R and 1R to Na\"{i}ve Bayes, decision trees, logistic regression,
$k$-nearest neighbour (and extensions K* and Ranked Distance), to the more
sophisticated support vector machines and multi-layer perceptrons. The reason
for our inclusion of so many algorithms is two-fold. Firstly, many of
these algorithms have not been extensively applied in various medical settings
to the problem of LOS prediction. Using a wide range of algorithms from various
paradigms will enable us to see what algorithms perform better than others.
Secondly, evaluating several classifiers will allow us to make comparisons
between different feature selection methods that are independent of the
classifier and give us more insight into the nature of the data set and of the
problem.

>>>>

\subsubsection{Ranked Distance}
\label{sec:rankeddist}
\paragraph{Intuition}
As we mentioned earlier, all features are considered equally in a $k$-NN
classifier, which implies that all features are equally important in predicting
the class. In practice, however, this is not always the case: to predict the
LOS of a trauma patient, the severity of their injury should affect the final
LOS more than whether or not they can speak English (which could be just two
of many features that are recorded about a patient). Our contribution is thus
a modified distance function to take the relative importance of attributes into
account.

@@

\section{Summary}
In this chapter we have outlined all of the learning algorithms that we will
be evaluating with respect to our classification problem, from the simple
0R and 1R to Na\"{i}ve Bayes, decision trees, logistic regression,
$k$-nearest neighbour (and extensions K* and Ranked Distance), to the more
sophisticated support vector machines and multi-layer perceptrons. The reason
for our inclusion of so many algorithms is two-fold. Firstly, many of
these algorithms have not been extensively applied in various medical settings
to the problem of LOS prediction. Using a wide range of algorithms from various
paradigms will enable us to see what algorithms perform better than others.
Secondly, evaluating several classifiers will allow us to make comparisons
between different feature selection methods that are independent of the
classifier and give us more insight into the nature of the data set and of the
problem.

### 2014-10-26 thesis/method/preprocess.tex
Added some section labels and updated some headings

\section{Conclusion}
In this chapter we discussed various issues encountered during the
preprocessing stage and how these were addressed. These steps are critical to
the success of our learning algorithms: without cleaned data, any subsequent
work is meaningless and difficult to draw valid conclusions from. By outlining
our steps, we hope to provide an example of how one can conduct the cleaning
process.

>>>>

The data was discretised according to the above method using the supervised
discretisation filter in WEKA. We keep both the original data set (without
discretisation) and the discretised data set for comparison.

\section{Summary}
In this chapter we discussed various issues encountered during the
preprocessing stage and how these were addressed. These steps are critical to
the success of our learning algorithms: without cleaned data, any subsequent
work is meaningless and difficult to draw valid conclusions from. By outlining
our steps, we hope to provide an example of how one can conduct the cleaning
process.

### 2014-10-26 thesis/method/selection.tex
Added some section labels and updated some headings

\section{Manual Selection}
All of the above automatic feature selection methods use some notion of
``relevance'', such as symmetric uncertainty and linear correlation,
in order to determine the best subset of features to select.
Depending on the problem at hand, these definitions of relevance may or may
not work well with the data. In the LOS prediction literature, studies
have enlisted the help of medical domain experts to assist in feature
selection, due to their experience and understanding of the underlying
problem and the effect of the features on the outcome. It will therefore be
worthwhile to compare the performance of classifiers using features selected
automatically and manually.

>>>>

\section{Manual Selection}
\label{sec:manual}
All of the above automatic feature selection methods use some notion of
``relevance'', such as symmetric uncertainty and linear correlation,
in order to determine the best subset of features to select.
Depending on the problem at hand, these definitions of relevance may or may
not work well with the data. In the LOS prediction literature, studies
have enlisted the help of medical domain experts to assist in feature
selection, due to their experience and understanding of the underlying
problem and the effect of the features on the outcome. It will therefore be
worthwhile to compare the performance of classifiers using features selected
automatically and manually.
